TKT RNAseq Experiment: Differential Expression Analysis

### 2023-06-23 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
upsdated app
fixed edger html

<br /><br /><br />
\newpage

@@

>>>>

- #### Figure \@ref(fig:fig15): Venn Diagram of total DEGs between male and female samples

Venn Diagram of total DEGs between male and female samples
<br /><br /><br />
\newpage

@@

##Removing genes that are too low expressed in Females frome the FxM DEGs
temp = apply(cpmdata2[, c(1:2,29:30)], 1, mean)
temp = temp[temp<4]
GR.FxM[names(temp),"FDR"] = .05
WT.FxM[names(temp),"FDR"] = .05
